### 2017-05-15 Publications/Original Software Publications/Science of Computer Programming/reply letter/letter.tex
updating reply letter
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: To be honest, I didn't get it. Do you think this is correct? Could professor Ricardo Pereira help us answer this question appropriately? Can you please check this with Isabela? Isabela had worked quite hard on the experimental evaluation and examples of our papers.}}
    \end{quote}

>>>>

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} Indeed, there was a code line missing from the figure, we have fixed it now.}
    \end{quote}
